The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2015-12-23 article.tex
More work

However, previous version of the CDK were written by a community with specific applications
in mind, of which structure elucidation was one. It could therefore be rather competitive
in some cheminformatics domains, such as fingerprinting~\cite{Ekins,Cannon}, in other parts
it could be inadequate, such in the capturing of stereochemistry.

@@

This has resulted in important improved functionality, such as a separately published
InChI functionality~\cite{SpjuthXXXX} and greatly improved ring detection functionality~\cite{MayYYYY},
but also a core atom type perception module, covering a much wider set of elements than
previous CDK versions and capturing many more charged and radical atom species,
a more comprehensive fingerprinting API, many speed and stability improvements, and more.

@@

  CDK 1.4.XXXX [CHECK] introduces a new API for stereochemistry information: the interfaces
  IStereoChemistryElement was introduced with ...

  New classes include:

@@

The chemical formula is the basic/simple chemical representation of a compound.
It defines the number of isotopes or elements that constitute a the composition
of a compound without describing how atoms are bonded. With the rise of metabolomics,
it has become increasingly relevant to have full support in cheminformatics
libraries~\cite{RojasChertoXXX}.
It is also the first step
toward the identification of the chemical structure from a unidentified compound.

@@

@@

Another change made over the past years is the move to a Git-based version
control system. Advantages the projects makes advantage of is the distributed
nature of Git repositories, and easier branching and making available of
patches. GitHub has replaced SourceForge as the main source code hosting service
where we can use novel approaches for commenting on code, pull requests, etc.
These new features simplify our code review process.

@@

\begin{itemize}
\item \textbf{Project Name}: The Chemistry Development Kit
\item \textbf{Project home page}: \url{http://cdk.sourceforge.net/}
\item \textbf{Operating system(s)}: Windows, GNU/Linux, OS/X
\item \textbf{Programming language}: Java
\item \textbf{Other (optional) requirements}: JNI-InChI, Vecmath, BEAM, Guava, JGraphT, Signatures, CMLDOM, XOM, JavaCC
\item \textbf{License}: LGPL v2.1 or later
\item \textbf{Any restrictions to use by non-academics}: None additional
\end{itemize}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip

>>>>

However, previous version of the CDK were written by a community with specific applications
in mind, of which structure elucidation was one. It could therefore be rather competitive
in some cheminformatics domains, such as fingerprinting~\cite{Clark2014,Cannon}, in other parts
it could be inadequate, such in the capturing of stereochemistry.

@@

This has resulted in important improved functionality, such as a separately published
InChI functionality~\cite{Spjuth2013} and greatly improved ring detection functionality~\cite{May2014},
but also a core atom type perception module, covering a much wider set of elements than
previous CDK versions and capturing many more charged and radical atom species,
a more comprehensive fingerprinting API, many speed and stability improvements, and more.

@@

  The new CDK version introduces a new API for stereochemistry information: the interfaces
  IStereoChemistryElement was introduced with the implementations TetrahedralChirality,
  for four coordinate compounds like bromo-chloro-fluoro-iodomethane,
  DoubleBondStereochemistry, for compounds like trans-2-butene, and
  ExtendedTetrahedral, for compounds like allene.

@@

The chemical formula is the basic/simple chemical representation of a compound.
It defines the number of isotopes or elements that constitute a the composition
of a compound without describing how atoms are bonded. With the rise of metabolomics,
it has become increasingly relevant to have full support in cheminformatics
libraries~\cite{RojasCherto2011}.
It is also the first step
toward the identification of the chemical structure from a unidentified compound.

@@

  .... \cite{May2014}

@@

Another change made over the past years is the move to a Git-based version
control system. Advantages the projects makes advantage of is the distributed
nature of Git repositories, and easier branching and making available of
patches. GitHub (\url{https://github.com/cdk/cdk}) has replaced SourceForge
as the main source code hosting service
where we can use novel approaches for commenting on code, pull requests, etc.
These new features simplify our code review process.

@@

\begin{itemize}
\item \textbf{Project Name}: The Chemistry Development Kit
\item \textbf{Project home page}: \url{https://github.com/cdk/cdk}
\item \textbf{Operating system(s)}: Windows, GNU/Linux, OS/X
\item \textbf{Programming language}: Java
% FIXME: add appropriate references below
\item \textbf{Other (optional) requirements}: JNI-InChI, Vecmath, BEAM, Guava, JGraphT, Signatures, CMLDOM, XOM, JavaCC
\item \textbf{License}: LGPL v2.1 or later
\item \textbf{Any restrictions to use by non-academics}: None additional
\end{itemize}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - The molecular fingerprints in CDK}
  \label{tab:fingerprints}
  Listed are the currently available molecular fingerprint in CDK with
  information about whether they come as bit / count versions, what CDK version
  they appeared in, their default size and where applicable also relevant
  references.
  \vskip 1\baselineskip
